A community-maintained standard library of population genetic models

### 2019-12-20 popSimManu.tex
capitalized stdpopsim when starting a sentence

Given the genome data and simulation model descriptions defined within the
library, it is then straightforward to run accurate, standardized simulations
across a range of organisms. \stdpopsim has a Python API and a user-friendly
command line interface, allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the ``tree sequence''
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed efficiently using the \tskit library
\citep{kelleher2016efficient,kelleher2018efficient}. Currently,
\stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine.
We have implemented \texttt{SLiM} \citep{haller2019tree,haller2019slim} 
as an alternative backend,
to allow simulation of processes that cannot be modeled under the coalescent.

@@

\stdpopsim allows us to readily compare relative performance on this benchmark to
that based on a different
model of human history. In Figure \ref{fig:n_t_gutenkunst} we show estimates of
$N(t)$ from simulations using the same physical and genetic maps, but from the OutOfAfrica\_3G09
demographic model that does not include archaic admixture. Again we see that each
of the methods is capturing relevant parts of the population history, although the
accuracy varies across time. In comparing inferences between the
models it is interesting to note that $N(t)$ estimates for the CHB and CEU
simulated populations are generally better across methods than estimates from the YRI
simulated population.

@@

\stdpopsim is intended to be a fully open, community-developed project.
Our implementations of genome representations and genetic maps for the some of
the most common study systems in computational genetics---humans, \textit{Drosophila},
and \textit{Arabidopsis} (among others)---are only intended to be a starting point for
future development.  In addition to other taxa,
we plan to incorporate other common biological processes
such as selection, gene conversion, and mutational heterogeneity.
Researchers are invited to contribute to the resource by adding their
organisms and models of choice. The \stdpopsim resource is
accompanied by clearly documented standard operating procedures that are
intended to minimize barriers to entry for new developers.  In this way, we
expect the resource to expand and adapt to meet the evolving needs of the
population genomics community.

>>>>

Given the genome data and simulation model descriptions defined within the
library, it is then straightforward to run accurate, standardized simulations
across a range of organisms. \Stdpopsim has a Python API and a user-friendly
command line interface, allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the ``tree sequence''
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed efficiently using the \tskit library
\citep{kelleher2016efficient,kelleher2018efficient}. Currently,
\stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine.
We have implemented \texttt{SLiM} \citep{haller2019tree,haller2019slim} 
as an alternative backend,
to allow simulation of processes that cannot be modeled under the coalescent.

@@

\Stdpopsim allows us to readily compare relative performance on this benchmark to
that based on a different
model of human history. In Figure \ref{fig:n_t_gutenkunst} we show estimates of
$N(t)$ from simulations using the same physical and genetic maps, but from the OutOfAfrica\_3G09
demographic model that does not include archaic admixture. Again we see that each
of the methods is capturing relevant parts of the population history, although the
accuracy varies across time. In comparing inferences between the
models it is interesting to note that $N(t)$ estimates for the CHB and CEU
simulated populations are generally better across methods than estimates from the YRI
simulated population.

@@

\Stdpopsim is intended to be a fully open, community-developed project.
Our implementations of genome representations and genetic maps for the some of
the most common study systems in computational genetics---humans, \textit{Drosophila},
and \textit{Arabidopsis} (among others)---are only intended to be a starting point for
future development.  In addition to other taxa,
we plan to incorporate other common biological processes
such as selection, gene conversion, and mutational heterogeneity.
Researchers are invited to contribute to the resource by adding their
organisms and models of choice. The \stdpopsim resource is
accompanied by clearly documented standard operating procedures that are
intended to minimize barriers to entry for new developers.  In this way, we
expect the resource to expand and adapt to meet the evolving needs of the
population genomics community.
